### 2020-01-15 cv_models.tex
minor reorg
updated images, can autogen now

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm ]{
        \includegraphics[width=5cm]{img/vgg-fnorm.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[ Spectral Norm ]{
        \includegraphics[width=4.9cm]{img/vgg-snorm.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha ]{
        \includegraphics[width=4.9cm]{img/vgg-walpha.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[ Alpha-Norm ]{
        \includegraphics[width=4.9cm]{img/vgg-pnorm.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of norm metrics vs reported test accuracy for pretrained VGG models, trained on ImageNet, available in pyTorch.  Plots will be updated and replace }

@@

    \subfigure[ ResNet ]{
        \includegraphics[width=4.2cm]{img/resnet-accuracy.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K ]{
        \includegraphics[width=4.5cm]{img/resnet1k-accuracy.png}
        \label{fig:resnet1k-accuracy}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.4cm]{img/densenet-accuracy.png}
        \label{fig:densenet-accuracy}
    }
    \caption{$\alpha$-Norm vs reported Top1 Error for  ResNet, ResNet-1K, and DenseNet models}
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & & & & \\
 ResNet & & & & \\
 ResNet-1K & & & & \\
 DenseNet & & & & \\
\hline
\end{tabular}
\end{center}
\caption{RMSE for Linear Fits of Metric to Reported Top1 Test Error for all pre-trained models in the architecture series.  All models trained on ImageNet except ResNet-1K, which was trained on ImageNet-1K. }
\label{table:models}
\end{table}

\paragraph{Correlations and Information Flow in CV Models}

@@

    \subfigure[ VGG ]{
        \includegraphics[width=4.1cm]{img/vgg-alpha-layers.png}
        \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet ]{
        \includegraphics[width=3.8cm]{img/resnet-alpha-layers.png}
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.1cm]{img/densenet-alpha-layers.png}
        \label{fig:densenet-alpha-layer}
    }
    \caption{Power law exponent $\alpha$ vs layer for VGG, ResNet, and DenseNet models}
    \label{fig:vgg-alpha-layers}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm ]{
        \includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[ Spectral Norm ]{
        \includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[ Alpha-Norm ]{
        \includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of norm metrics vs reported test accuracy for pretrained VGG models, trained on ImageNet, available in pyTorch.  Plots will be updated and replace }

@@

    \subfigure[ ResNet ]{
        \includegraphics[width=4.2cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K ]{
        \includegraphics[width=4.5cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.4cm]{img/DenseNet_logpnorm_accs.png}
        \label{fig:densenet-accuracy}
    }
    \caption{$\alpha$-Norm vs reported Top1 Error for  ResNet, ResNet-1K, and DenseNet models}
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & & & & & \\
 ResNet & & & & & \\
 ResNet-1K & & & & & \\
 DenseNet & & & &  &\\
\hline
\end{tabular}
\end{center}
\caption{RMSE for Linear Fits of Metric to Reported Top1 Test Error for all pre-trained models in the architecture series.  All models trained on ImageNet except ResNet-1K, which was trained on ImageNet-1K. }
\label{table:models}
\end{table}

\paragraph{Correlation Flow in CV Models}

Explain WHAT IS \emph{Correlation Flow}

@@

    \subfigure[ VGG ]{
        \includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet ]{
        \includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.5cm]{img/DenseNet_all_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{Power law exponent $\alpha$ vs layer for VGG, ResNet, and DenseNet models}
    \label{fig:vgg-alpha-layers}
\end{figure}

### 2020-01-15 nlp_models.tex
updated images, can autogen now

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & \\
 GPT2 (small) & & & & \\
 GPT2-medium & & & & \\
 GPT2-large & & & & \\
 GPT2-xl & & & & \\

@@

\begin{figure}
   \includegraphics[scale=0.25]{img/gpt-alpha-hist.png}
   \caption{Comparison of heavy tailed power law exponent $\alpha$ for OpenAI GPT and GPT pretrained models}

   \label{fig:gpt-alphs-hist}
\end{figure}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.0cm]{img/gpt-alpha-layer.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/gpt-snorm-layer.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/gpt-pnorm-layer.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/gpt2-alpha-hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/gpt2-snorm-hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/gpt2-pnorm-hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.    }
    \label{fig:gpt-alpha-layers}
\end{figure}

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
 GPT2 (small) & & & & & \\
 GPT2-medium & & & & & \\
 GPT2-large & & & & & \\
 GPT2-xl & & & & &\\

@@

\begin{figure}
   \includegraphics[scale=0.25]{img/gpt-alpha-hist.png}
   \caption{Comparison of heavy tailed power law exponent $\alpha$ for OpenAI GPT and GPT pretrained models}
   \label{fig:gpt-alpha-hist.png}
\end{figure}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT-alpha-depth.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT-snorm-depth.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT-pnorm-depth.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT2_fnl_alpha_hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT2_fnl_spectralnorm_hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT2_fnl_alpha_weighted_hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.    }
    \label{fig:gpt-alpha-layers}
\end{figure}
